Racets: Embedding Policy{-}Agnostic Programming in Racket

### 2018-07-19 paper/paper.tex
adding more semantics stuff..

\usepackage{booktabs} % For formal tables
\usepackage[linguistics]{forest}
\usepackage{tikz}
\usetikzlibrary{cd}

\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

@@

%% To color math, put it in an \mc command, e.g., \mc{$a$}
\newcommand{\colorMATH}{black!20!blue}
\newcommand{\blue}[1] {{\color{\colorMATH} #1}}
\newcommand{\bmth}[1] {{\color{\colorMATH} $#1$}}
\newcommand{\code}[1]{\lstinline{#1}}

\newcommand{\comm}[3][\color{red}]{{#1{[{#2}: {#3}]}}}
\newcommand{\zw}[1]{\comm[\color{green!66!black}]{Zhanpeng}{#1}}
\newcommand{\kris}[1]{\comm[\color{blue}]{Kris}{#1}}
\newcommand{\tom}[1]{\comm[\color{orange}]{Tom}{#1}}
\newcommand{\lang}[0]{$\lambda_\textsc{FE}$\xspace}
\newcommand{\facet}[3]{\blue{${\langle \, {#1} \: ? \: {#2} \diamond \: {#3} \, \rangle}$}}

@@

>>>>

\usepackage{booktabs} % For formal tables
\usepackage[linguistics]{forest}
\usepackage{tikz}
\usetikzlibrary{cd}
\usepackage{xcolor}
\usepackage{mathpartir} % Inference rules
\usepackage[ruled]{algorithm2e} % For algorithms
\renewcommand{\algorithmcfname}{ALGORITHM}
\SetAlFnt{\small}
\SetAlCapFnt{\small}
\SetAlCapNameFnt{\small}
\SetAlCapHSkip{0pt}
\IncMargin{-\parindent}

@@

%% To color math, put it in an \mc command, e.g., \mc{$a$}
\newcommand{\colorMATH}{black!20!blue}
\newcommand{\colorFAC}{black!20!red}
\newcommand{\blue}[1] {{\color{\colorMATH} #1}}
\newcommand{\fcol}[1] {{\color{\colorFAC} #1}}
\newcommand{\bmth}[1] {{\color{\colorMATH} $#1$}}
\newcommand{\code}[1]{\lstinline{#1}}

\newcommand{\comm}[3][\color{red}]{{#1{[{#2}: {#3}]}}}
\newcommand{\zw}[1]{\comm[\color{green!66!black}]{Zhanpeng}{#1}}
\newcommand{\kris}[1]{\comm[\color{blue}]{Kris}{#1}}
\newcommand{\tom}[1]{\comm[\color{orange}]{Tom}{#1}}
\newcommand{\lang}[0]{$\lambda_\textsc{FE}$\xspace}
\newcommand{\facet}[3]{{\fcol{\ensuremath{\langle \, {#1} \: ? \: {#2} \diamond \: {#3} \, \rangle}}}}
\newcommand{\formfacet}[3]{{\fcol{\ensuremath{\langle \langle \, {#1} \: ? \: {#2} \diamond \: {#3} \,  \rangle \rangle}}}}

@@

\section{A Formal Semantics for Faceted Execution}

\begin{figure}
\begin{displaymath}
  \begin{array}{lcrcl}
    \blue{c} & \blue{\in} & \blue{const} & \blue{::=} & \blue{() \mid \code{\#t} \mid \code{\#f} \mid \ldots} \\
    \blue{x} & \blue{\in} & \blue{var} & \blue{::=} & \blue{\ldots}  \\
    \blue{e} & \blue{\in} & \blue{exp} & \blue{::=} & \blue{c} \mid \blue{x} \\
    & & & \blue{\mid} & \blue{(\lambda ~ (x) ~ e) \mid (e ~ e)} \\
    & & & \blue{\mid} & \blue{(\code{box} ~ e) \mid (\code{unbox} ~ e) \mid (\code{set!} ~ e ~ e)} \\
    & & & \blue{\mid} & \blue{(\code{let-label} ~ \ell ~ e ~ e)} \\
    & & & \blue{\mid} & \blue{(\code{facet} ~ e ~ e ~ e)} \\
    & & & \blue{\mid} & \blue{(\code{obs} ~ e ~ e ~ e)} \\
  \end{array}
\end{displaymath}
\label{fig:syntax}
\caption{Syntax of \lang}
\end{figure}

We now present a semantics for a core language (\lang) which includes
facets. Our presentation largely mirrors that of Austin et
al.~\cite{Austin:2013}. The syntax of our language---reminiscent of
Scheme---is shown in Figure~\ref{fig:syntax}. \lang extends the lambda
calculus with references (which have interact with facets in a subtle
way) and three forms unique to faceted execution: label creation,
facet construction, and facet observation.

\begin{figure*}
    \begin{tabular}{cc}
      \begin{minipage}{.5\textwidth}
        \begin{displaymath}
          \begin{array}{rcrcl}
            \blue{\alpha} & \blue{\in} & \blue{\text{addr}} & \blue{=} & \blue{\ldots} \\
            \blue{bv} & \blue{\in} & \blue{\text{base-val}} & \blue{::=} & \blue{c \mid \alpha \mid \langle \lambda x.~ e, \rho \rangle \mid \star}\\
            \fcol{v} & \blue{\in} & \blue{\text{faceted-val}} & \blue{::=} & \blue{bv \mid} ~ \fcol{\facet{\blue{\alpha}}{v}{v}}
            \\
          \end{array}
        \end{displaymath}
      \end{minipage}
      &
      \begin{minipage}{.5\textwidth}
        \begin{displaymath}
          \begin{array}{rcrcl}
            \blue{\alpha} & \blue{\in} & \blue{\text{addr}} & \blue{=} & \blue{\ldots} \\
            \blue{bv} & \blue{\in} & \blue{\text{base-val}} & \blue{::=} & \blue{c \mid \alpha \mid \langle \lambda x.~ e, \rho \rangle \mid \star}\\
            \blue{fv} & \blue{\in} & \blue{\text{facet-val}} & \blue{::=} & %% \blue{bv \mid \facet{\alpha}{fv}{fv}}
            \\
          \end{array}
        \end{displaymath}
      \end{minipage}
    \end{tabular}
    \\
    \hfill \boxed{\blue{e, \rho, \sigma \Downarrow_{pc}^E \sigma, v}}
    \\
    \begingroup
    \color{\colorMATH}
    \begin{displaymath}
      \begin{array}{c}
        \begin{array}{cccc}
          \inferrule[\textsc{Const}]{ }
                    {c, \rho, \sigma \Downarrow_{pc}^E \sigma, c}
                    & 
                    \inferrule[\textsc{Var}]{ }
                              {x, \rho, \sigma \Downarrow_{pc}^E \sigma, \rho(x)}
                              & 
                              \inferrule[\textsc{Lambda}]{ }
                                        {\lambda x. ~ e, \rho, \sigma \Downarrow_{pc}^E \sigma, \langle \lambda x. ~ e, \rho \rangle}
                                        &
        \end{array}
        \\
        \begin{array}{ccc}
          \inferrule[\textsc{Box}]
                    {e, \rho, \sigma \Downarrow_{pc}^E v, \sigma' \\\\
                      \alpha \not\in dom(\sigma') \\\\
                      \sigma'' = \sigma' [\alpha \mapsto \formfacet{pc}{v}{\star}]}
                    {(\code{box} ~ e), \rho, \sigma \Downarrow_{pc}^E v, \sigma''}
                    & 
          \inferrule[\textsc{Unbox}]
                    {e, \rho, \sigma \Downarrow_{pc}^E v, \sigma' \\\\
                     v' = \fcol{read(\sigma',v,pc)}}
                    {(\code{unbox} ~e), \rho, \sigma \Downarrow_{pc}^E v', \sigma'}
                    & 
          \inferrule[\textsc{Set}]
                    {e_1, \rho, \sigma \Downarrow_{pc}^E v_1, \sigma' \\\\
                     e_2, \rho, \sigma' \Downarrow_{pc}^E v_2, \sigma'' \\\\
                     \sigma''' = \fcol{write(\sigma'', v_1, pc, v_2)}}
                    {(\code{set!} ~ e_1 ~ e_2), \rho, \sigma \Downarrow_{pc}^E \sigma''', v_2}
        \end{array}
        \\
        \begin{array}{ccc}
          {\color{\colorFAC}
          \inferrule[\textsc{Let-Label}]
          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', v \\\\
           \alpha \not\in dom(\sigma) \and \sigma' = \sigma [\alpha \mapsto v] \\\\
           e_2, \rho [ \ell \mapsto \alpha ], \sigma' \Downarrow_{pc}^E \sigma'', v'}
          {(\code{let-label} ~ \ell ~ e_1 ~ e_2), \rho, \sigma \Downarrow_{pc}^E \sigma'', v'}}
          & 
          {\color{\colorFAC}
          \inferrule[\textsc{Fac-Create}]
          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', l \\\\
           e_2, \rho, \sigma' \Downarrow_{pc \cup \{+l\}}^E \sigma'', v_1 \\\\
           e_3, \rho, \sigma'' \Downarrow_{pc \cup \{-l\}}^E \sigma''', v_2 }
          {(\code{fac} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma''', \formfacet{pc}{v_1}{v_2}}}
          & 
          {\color{\colorFAC}
          \inferrule[\textsc{Obs}]
          {e_1, \rho, \sigma \Downarrow_{pc}^E \sigma', \ell \\\\
           e_2, \rho, \sigma' \Downarrow_{pc}^E \sigma'', v  \\\\
           \langle (\lambda x.~e), \rho' \rangle = \sigma''(\ell) \\\\
           e_3, \rho' [x \mapsto v], \sigma'' \Downarrow_{pc}^E \sigma''', v'}
          {(\code{obs} ~ e_1 ~ e_2 ~ e_3), \rho, \sigma \Downarrow_{pc}^E \sigma''' v'}}
        \end{array}
      \end{array}
    \end{displaymath}
              %%\inferrule[]
    \endgroup
\end{figure*}
